Current State of Knowledge Representation Systems for Robotics

### 2011-11-21 paper.tex
More on PEIS Ecology

In short:
* Roughly the same kind of ambition and architecture.
* Way better than us on the perception side. 
* They try the "2nd order logic" approach. I'd be curious to know what kind of reasoning capability they actually have.
* Their tests are conducted in a static environment. They don't take other agents into consideration (nothing like perspective taking or rich disambiguation).
* No task planning at all (or at least, not discussed in this paper)

@@

\subsubsection{Integration in the PEIS Ecology architecture}
\label{sect|peis-integration}

\begin{figure}
	\centering
	\includegraphics[width=0.9\columnwidth]{peis-architecture.pdf}
	\caption{The PEIS knowledge representation system, taken from~\cite{Daoutis2009}}
	\label{fig|peis-architecture}
\end{figure}

The PEIS KR\&R system is deeply integrated to the general PEIS Ecology environment.

>>>>

@@

\paragraph{Expressiveness} The PEIS Knowledge representation system relies on
the {\sc ReseachCyc} and {\sc CycL} language to represent knowledge. The {\sc CycL} language
allows to represent first order logic sentences and has extensions for modal logics and higher order logics.

\fxfatal{Is modal logics and higher order logics actually used in PEIS?}

As a system relying on {\sc CycL}, contexts can be expressed as
\emph{microtheories}: the truth or falsity of a set of statement depends of the
\emph{microtheory} in which these statements are evaluated.

\fxfatal{OWA/CWA?}

\subsection{Anchoring strategies}
\label{sect|peis-anchoring}

\begin{figure}
	\centering
	\includegraphics[width=0.9\columnwidth]{peis-architecture.pdf}
	\caption{The PEIS knowledge representation system, taken from~\cite{Daoutis2009}}
	\label{fig|peis-archi}
\end{figure}

The PEIS KR\&R system is deeply integrated to the general PEIS Ecology
\emph{smart} environment. Figure~\ref{fig|peis-archi} gives an overview of the
interactions between PEIS knowledge processing layers.

\paragraph{Knowledge Acquisition} The primary source for knowledge acquisition
is perception.  The PEIS ecosystem provides a SIFT-based object recognizer used
in conjunction with ceiling cameras for object localization.  Other perceptual
modalities are available (like human tracking, ambient environment monitoring).

A template-based natural language parsing system may also be used to add new
assertions to the system.

\paragraph{Anchoring} Daoutis et al. formalize the issue of anchoring as
finding a \emph{predicate grounding relation} $g \subseteq \mathcal{P} \times
\Phi \times D(\Phi)$, where $\mathcal{P}$ is a set of predicate symbols, $\Phi$
a set of percept's attributes, and $D(\Phi)$ the domain of these attributes.

In the current implementation, object category (returned by the SIFT
classifier), color, location, spatial relations (both topological -- \emph{at},
\emph{near} -- and relative to the robot -- \emph{left}, \emph{behind}, etc.)
and visibility are the five classes of extracted attributes.

\subsubsection{Integration in the robot architecture}
\label{sect|peis-integration}

The PEIS framework offers through the \emph{PEIS middleware} a practical way to
insert a new component into the shared \emph{tuple space}.  Thus, the KR\&R
module can be seemlessly integrated into the PEIS ecosystem.

\subsubsection{Notable experiments}
\label{sect|peis-expe}
